Effect of Beam Chromaticity on Foregrounds in Wide-Field Measurements of Redshifted 21~cm Power Spectra

### 2016-03-05 ForegroundSimulations/ms.tex
Update Summary section
From d67699b (fgsim):
====================

In ms.tex,

(*) Update Summary section

\acknowledgments

This work was supported by the U. S. National Science Foundation (NSF) through award AST-1109257.

>>>>

First-generation EoR experiments such as the MWA, PAPER and LOFAR have made enormous progress in the field of 21~cm cosmology. However, they are currently limited by the systematics due to the extremely bright foregrounds and the instrument. Hence, characterizing the foregrounds and the instrument to a very high level of precision is critical for the success of next-generation EoR experiments. In this paper, we highlight the importance of a key systematic feature of the instrument -- the spectral structure of the antenna power pattern -- and its impact on EoR signal contamination, using HERA as an example.

Using a new high dynamic range spectral weighting function obtained by convolving a {\it Blackman-Harris} window with itself, we isolate the effects of beam chromaticity on foreground delay power spectrum. We use three antenna beam models of varying chromaticity (achromatic, {\it Airy} and simulated chromatic) and show that increase in chromaticity extends the foreground spillover well beyond the horizon limits of the {\it foreground wedge} into the clean {\it EoR window} considered sensitive for EoR signal detection. The level of foreground spillover in the simulated chromatic beam is a few orders of magnitude worse than that from a nominal {\it Airy} disk pattern, which in turn is many orders of magnitude worse than that from an achromatic beam with no spectral structure.

We note that the inevitable reflections in the antenna-feed assembly and between reflecting structures across multiple antennas are also significant factors that contaminate the cosmological signal in high $k_\parallel$-modes inside the {\it EoR window}. Using a novel approach, we provide a formalism to set cosmologically-motivated constraints directly on the level of suppression required on these reflections in the instrument. Ongoing reflectometry studies clearly indicate HERA will exceed the cosmologically-motivated lower limits prescribed here.

Taking into account the effects of these instrumental systematics, if data is not limited by thermal noise, we demonstrate that HERA will detect EoR with high significance with s simple spectral weighting even under a conservative analysis criterion which does not involve any {\it foreground removal} strategies. All baselines of HERA-19 will not only detect but also help in filtering highly likely EoR models.

We are also investigating advanced strategies for foreground removal that will robustly eliminate these systematics further. More optimal analysis techniques and further design improvements will make HERA not only clear the obstacles limiting first-generation experiments but also become transformational for next-generation low frequency cosmology experiments.

% \acknowledgments

% This work was supported by the U. S. National Science Foundation (NSF) through award AST-1109257.
